\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.85in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}

\definecolor{accent}{RGB}{31,78,121}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\vspace{-0.6em}\color{accent}\hrule\vspace{0.4em}]
\titlespacing{\section}{0pt}{1.2em}{0.4em}

\setlist[itemize]{leftmargin=1.4em, itemsep=1pt, topsep=2pt}

\newcommand{\role}[4]{%
  \noindent\textbf{#1} \hfill \textit{#3}\\
  \textit{#2} \hfill #4\\[0.2em]
}

\pagestyle{empty}

\begin{document}

\begin{center}
  {\Huge \textbf{Rohith Kumar Seetha}}\\[0.3em]
  {\large Senior Full Stack Engineer \;|\; TypeScript \(\bullet\) Node.js \(\bullet\) React \(\bullet\) AWS}\\[0.3em]
  Melbourne, Australia \;|\; \href{mailto:rohithseetha@gmail.com}{rohithseetha@gmail.com} \;|\; +61 401 415 174\\
  \href{https://linkedin.com/in/rohith-seetha-8272b11b}{linkedin.com/in/rohith-seetha-8272b11b} \;|\;
  \href{https://github.com/rohithseetha}{github.com/rohithseetha}\\[0.3em]
  \textbf{\color{accent}Australian Permanent Resident (Subclass 190) --- Open to Sydney relocation --- Available Immediately}
\end{center}

\section*{Professional Summary}
Senior full stack engineer with 14+ years building scalable, customer-facing applications at large scale. Strong
commercial depth across TypeScript, Node.js, React, and AWS, with a track record of designing scalable systems and
APIs, driving architectural decisions and engineering best practices, and mentoring engineers to uplift team
capability. Comfortable operating across architecture, hands-on delivery, and stakeholder engagement in
fast-moving, product-led environments. Also an AI-native engineer --- daily Claude Code user who has shipped
production LLM agents over enterprise APIs (Azure AI Foundry), with hands-on work in system-prompt design,
adapting OpenAPI specs into agent tool definitions, multi-vendor model integration, and multi-step agent
orchestration. Australian PR (Subclass 190), open to Sydney relocation, available immediately.

\section*{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textbf{Languages} & TypeScript, JavaScript, Node.js, Python, Java (Spring Boot), SQL \\
  \textbf{Frontend} & React (functional components, hooks, state management), Next.js, responsive design, CSS \\
  \textbf{Backend \& APIs} & Node.js (Express), Python (FastAPI), REST \& GraphQL, OpenAPI / contract-first design, API security, microservices \\
  \textbf{Agentic AI \& LLMs} & LLM agents, agent orchestration, multi-vendor model integration, system-prompt design, OpenAPI specs adapted into agent tool definitions, Azure AI Foundry, Anthropic Claude API, Model Context Protocol (MCP) \\
  \textbf{Agent Frameworks} & LangChain / LangGraph --- exploratory, actively deepening; orchestration patterns transferable from Azure AI Foundry agent work \\
  \textbf{AWS Cloud} & Lambda (serverless), ECS (containers), RDS, DynamoDB, S3, EC2, IAM, VPC, CloudWatch \\
  \textbf{Architecture} & Scalable system design, distributed \& event-driven systems (Kafka), design patterns, performance optimisation \\
  \textbf{Security} & OAuth2, OIDC, JWT, RBAC, Azure AD, application \& cloud security \\
  \textbf{DevOps \& Delivery} & CI/CD pipelines, Docker, Kubernetes, GitOps, observability (Datadog, Sentry, OpenSearch) \\
  \textbf{Databases} & PostgreSQL, MySQL, MongoDB, DynamoDB, schema design, migrations \\
  \textbf{Leadership} & Mentoring, code review, architectural decisions, stakeholder engagement, technical design \\
  \textbf{AI-Assisted Engineering} & Claude Code (daily), Anthropic Claude API, GitHub Copilot, LLM agents over enterprise APIs, Azure AI Foundry \\
\end{tabularx}

\section*{Professional Experience}

\role{Senior Full Stack Engineer --- AI, Blockchain \& Distributed Systems}{Ericsson}{June 2025 -- April 2026}{Stockholm, Sweden}
\begin{itemize}
  \item Built TypeScript / Node.js and Python (FastAPI) backend services, microservices, and React frontends on AWS and Azure.
  \item Designed scalable REST and GraphQL APIs consumed by 50+ engineers --- schema-first, versioned, secured with OAuth2 / OIDC, with strong backward-compatibility guarantees.
  \item Drove architectural decisions and engineering best practices; contributed to technical design and API definition across platform teams.
  \item Built Kafka-based event-driven services processing high-throughput data flows across distributed components.
  \item Containerised services with Docker / Kubernetes and delivered through CI/CD pipelines with unit and integration testing.
  \item Built production LLM agents over enterprise APIs using Azure AI Foundry --- system-prompt design, OpenAPI specs adapted into agent tool definitions, and multi-step agent orchestration (ID-chaining across program \(\to\) package \(\to\) evidence sequences); use Claude Code daily.
  \item Integrated LLMs and models from multiple vendors behind a secure, scalable enterprise platform, adapting external API specs into agent-consumable tools across orchestration layers.
  \item Partnered directly with customer and partner technical teams to understand needs and shape agentic solutions.
  \item Mentored engineers and uplifted team capability through pairing, documentation, and code review.
\end{itemize}

\role{Full Stack Engineer --- Commerce \& Mobility SaaS Platform}{Brick Technology AB}{September 2023 -- May 2025}{Stockholm, Sweden}
\begin{itemize}
  \item Shipped customer-facing full-stack features end-to-end --- React / TypeScript frontends and Node.js / Python backend services on AWS.
  \item Built real-time React dashboards (SSE) streaming live operational data; re-engineered backends for higher concurrency and larger payloads, with strong state management and responsive design.
  \item Delivered production payment integrations (Stripe, Monri, Flutterwave) with idempotency, retry, and reconciliation.
  \item Owned an observability platform migration (Datadog \(\to\) Sentry) and a production DynamoDB \(\to\) PostgreSQL migration --- schema modelling, data migration, and cutover.
  \item Collaborated closely with Product, design, and operations in small senior product teams.
\end{itemize}

\role{Assistant Consultant --- Enterprise Integration \& Distributed Platforms}{Tata Consultancy Services Ltd}{July 2019 -- September 2023}{India}
\begin{itemize}
  \item Designed and delivered backend services, REST APIs, and microservices for large-scale enterprise integration projects.
  \item Architected ERP integration solutions (SAP, Oracle) --- middleware, data transformation, and API interfaces across enterprise platforms.
  \item Implemented blockchain applications on Hyperledger Fabric and R3 Corda; filed a patent for a Blockchain-Driven Informer Ecosystem.
  \item Ran client-facing technical engagements with enterprise stakeholders across integration projects.
  \item Automated CI/CD pipelines, enforced code review standards, and mentored engineers across delivery teams.
\end{itemize}

\role{IT Analyst --- Enterprise Platforms \& Integration}{Tata Consultancy Services Ltd}{December 2015 -- July 2019}{India}
\begin{itemize}
  \item Developed enterprise backend systems and integration layers connecting Oracle ERP data with downstream operational and reporting systems.
  \item Collaborated with cross-functional teams in Agile delivery to translate business requirements into scalable solutions.
\end{itemize}

\role{Senior Software Engineer}{Foray Software Pvt Ltd}{April 2015 -- December 2015}{Hyderabad, India}
\begin{itemize}
  \item Developed scalable enterprise applications using API-centric architectures.
\end{itemize}

\role{Senior Software Engineer}{IGate}{May 2014 -- April 2015}{Hyderabad, India}
\begin{itemize}
  \item Delivered enterprise backend services; resolved complex production issues and improved reliability.
\end{itemize}

\role{Senior Software Engineer}{Tech Mahindra}{April 2011 -- May 2014}{Hyderabad, India}
\begin{itemize}
  \item Built enterprise software systems supporting mission-critical applications; designed scalable backend services.
\end{itemize}

\section*{Education}
\noindent\textbf{Bachelor of Technology (B.Tech)} \hfill 2006 -- 2010\\
\textit{Kakatiya Institute of Technology and Sciences}\\[0.4em]
\noindent\textbf{Post Graduate Diploma in Advanced Computing} \hfill 2010 -- 2011\\
\textit{Centre for Development of Advanced Computing (CDAC)}

\section*{Certifications}
\noindent\textbf{R3 Corda Certified Developer} \hfill 2020 -- Present

\section*{Achievements}
\noindent\textbf{Patent Filed} --- \textit{Blockchain Driven Informer Ecosystem for Public Safety and Crime Prevention}\\
Filed under Indian jurisdiction during tenure at Tata Consultancy Services.

\section*{Languages}
\textbf{English} --- Full Professional Proficiency \;|\; \textbf{Hindi} --- Professional Working Proficiency \;|\; \textbf{Telugu} --- Native / Bilingual Proficiency

\end{document}
